Assignment 3

### 2019-07-31 ex3/report/report.tex
Fixed labels
Fixed PDP text

\begin{table}[b]
\caption{Occurence probability of attack types.} \label{tab:performance_results}
\begin{tabular}{l r} \toprule
Attack type & Proportion \\
\midrule
Normal                                                         & $0.747468$ \\
DoS / DDoS:DoS Hulk                                            & $0.101014$ \\
PortScan:PortScan - Firewall off                               & $0.069020$ \\
DDoS:LOIT                                                      & $0.040784$ \\
Infiltration:Dropbox download & $0.032982$ \\
DoS / DDoS:DoS GoldenEye                                       & $0.003224$ \\
DoS / DDoS:DoS Slowhttptest                                    & $0.001819$ \\
DoS / DDoS:DoS slowloris                                       & $0.001680$ \\
Brute Force:SSH-Patator                                        & $0.001107$ \\
Botnet:ARES                                                    & $0.000327$ \\
Web Attack:XSS                                                 & $0.000293$ \\
PortScan:PortScan - Firewall on                                & $0.000165$ \\
Brute Force:FTP-Patator                                        & $0.000110$ \\
Web Attack:Sql Injection                                       & $0.000006$ \\
DoS / DDoS:Heartbleed                                          & $0.000001$ \\
\bottomrule
\end{tabular}
\label{tab:occurence}
\end{table}

@@

In particular,  \autoref{fig:pdps} shows the Partial Dependency Plots (PDP) for the source and destination port features. If $\boldsymbol X \in \mathbb R ^n$ denotes a random vector drawn from feature space and $f(X) \in [0,1]$ denotes the neural network's prediction, the PDP for feature $i$ can be defined as 
\begin{equation} \label{eq:pdp}
\text{PDP}_i(y) = \mathbb E_{\boldsymbol X}\left(f(X_1,\ldots,X_{i-1},y,X_{i+1},\ldots X_n)\right)
\end{equation}

As apparent from \autoref{pdp}, for a certain value of the $i$th feature, the whole dataset is used for averaging the neural network's outcome.

We also experiment with a modified definition of the PDP (with C being the distribution of attack classes): 
\begin{equation} \label{eq:pdp_conditional}
\text{PDP}_{c,i}(y) = \mathbb E_{\boldsymbol X | C = c} \left(f \left( X_1,\ldots,X_{i-1},y,X_{i+1},\ldots X_n \right) \right)
\end{equation}

@@

@@

The method minimizes the adversarial sample's distance so that the network's decision is just between attack and normal traffic. In the present context, we need to make sure that the classifer's prediction would actually be normal traffic, even though a certain level of noise will be added to interarrival times due to the network between attacker and victim. Instead of the above equation \ref{eq:carliniWagner} we therefore used the optimization objective
\begin{equation} \label{eq:carliniWagner}
d(X,\tilde X) + \epsilon  \max(Z(\tilde X), -0.2),
\end{equation}
i.e. we require a slight level of confidence that our adversarial samples are not classified as attack traffic.

>>>>

\begin{table}[b]
\caption{Occurence probability of attack types.} 
\begin{tabular}{l r} \toprule
Attack type & Proportion \\
\midrule
Normal                                                         & $0.747468$ \\
DoS / DDoS:DoS Hulk                                            & $0.101014$ \\
PortScan:PortScan - Firewall off                               & $0.069020$ \\
DDoS:LOIT                                                      & $0.040784$ \\
Infiltration:Dropbox download & $0.032982$ \\
DoS / DDoS:DoS GoldenEye                                       & $0.003224$ \\
DoS / DDoS:DoS Slowhttptest                                    & $0.001819$ \\
DoS / DDoS:DoS slowloris                                       & $0.001680$ \\
Brute Force:SSH-Patator                                        & $0.001107$ \\
Botnet:ARES                                                    & $0.000327$ \\
Web Attack:XSS                                                 & $0.000293$ \\
PortScan:PortScan - Firewall on                                & $0.000165$ \\
Brute Force:FTP-Patator                                        & $0.000110$ \\
Web Attack:Sql Injection                                       & $0.000006$ \\
DoS / DDoS:Heartbleed                                          & $0.000001$ \\
\bottomrule
\end{tabular}
\label{tab:occurence}
\end{table}

@@

In particular,  in literature the use of Partial Dependency Plots (PDP) is proposed. If $\boldsymbol X \in \mathbb R ^n$ denotes a random vector drawn from feature space and $f(X) \in [0,1]$ denotes the neural network's prediction, the PDP for feature $i$ can be defined as 
\begin{equation} \label{eq:pdp}
\text{PDP}_i(y) = \mathbb E_{\boldsymbol X}\left(f(X_1,\ldots,X_{i-1},y,X_{i+1},\ldots X_n)\right)
\end{equation}

To capture similarity between attack families, we in this research experiment with a modified definition of the PDP  (with C being the attack classes): 
\begin{equation} \label{eq:pdp_conditional}
\text{PDP}_{c,i}(y) = \mathbb E_{\boldsymbol X | C = c} \left(f \left( X_1,\ldots,X_{i-1},y,X_{i+1},\ldots X_n \right) \right)
\end{equation}

@@

As apparent from \autoref{eq:pdp}, for a certain value of the $i$th feature, the whole dataset is used for averaging the neural network's outcome.

@@

The method minimizes the adversarial sample's distance so that the network's decision is just between attack and normal traffic. In the present context, we need to make sure that the classifer's prediction would actually be normal traffic, even though a certain level of noise will be added to interarrival times due to the network between attacker and victim. Instead of the above equation \ref{eq:carliniWagner} we therefore used the optimization objective
\begin{equation} 
d(X,\tilde X) + \epsilon  \max(Z(\tilde X), -0.2),
\end{equation}
i.e. we require a slight level of confidence that our adversarial samples are not classified as attack traffic.
